The Concurrent Calculi Formalisation Benchmark

### 2024-01-25 short-paper/short-paper.tex
Fix some mistakes in references.

Several papers in this realm already include mechanised proofs
(e.g.~\cite{DBLP:conf/pldi/Castro-Perez0GY21,DBLP:conf/tacas/CastroFY20,lmcs:9985,
  DBLP:journals/jar/CruzFilipeMP23, Tirore:2023}), or discuss proof mechanisation techniques
(e.g.~\cite{DBLP:journals/jar/BengtsonPW16, DBLP:conf/tphol/Gay01,
  DBLP:conf/ppdp/Thiemann19, DBLP:conf/forte/ZalakainD21}).  Our
experience, however, is that choosing the appropriate proof mechanisation techniques and 
tools remains a significant challenge with a limited understanding of their 
respective tradeoffs.  This often leads researchers toward a trial-and-error approach, 
resulting in sub-optimal and ad-hoc solutions. In turn, this increases the overall effort 
required for proof mechanisation, and hampers the reuse of techniques and results.
%
It is therefore our view that the research community in message-passing
concurrency (and process calculi, more specifically) will benefit from a standardised set
of challenge probems.

>>>>

Several papers in this realm already include mechanised proofs
(e.g.~\cite{Castro-Perez2021,Castro2020,lmcs:9985,
  DBLP:journals/jar/CruzFilipeMP23, Tirore:2023}), or discuss proof mechanisation techniques
(e.g.~\cite{Bengtson2016, Gay2001,
  Thiemann2019, DBLP:conf/forte/ZalakainD21}).  Our
experience, however, is that choosing the appropriate proof mechanisation techniques and 
tools remains a significant challenge with a limited understanding of their 
respective tradeoffs.  This often leads researchers toward a trial-and-error approach, 
resulting in sub-optimal and ad-hoc solutions. In turn, this increases the overall effort 
required for proof mechanisation, and hampers the reuse of techniques and results.
%
It is therefore our view that the research community in message-passing
concurrency (and process calculi, more specifically) will benefit from a standardised set
of challenge probems.
